IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
capture
minor

An interesting aspect of JavaScript, as specified by
ECMAScript~\cite{ecma}, is that it does not have any built-in
functionality for I/O.
%
(We denote this language as |targetLangJS|.)
%
Instead, when embedding a JavaScript engine, browser layout engines,
such as Gecko, and server-side platforms, such as Node.js, expose APIs
such as the DOM and filesystem as part of the runtime system.
%
In a similar manner, we can directly implement the embedded language
|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
of the runtime and running multiple instances of the JavaScript VM in
separate OS-level threads.\footnote{
  We, indeed, do this for the Gecko implementation when considering
  Web Workers that run operate OS threads.
}
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
(Consider, for instance, a server-side web application that wishes to
create a new task for each HTTP request.)

@@

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks.}
\end{figure}
As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
by the trusted library code (the main Node.js context), that tracks
the current label, messages, etc. of each task.
%
While V8 provides a means for sharing objects between contexts that
share a security token (in the case of Blink this is used by pages of
the same origin), our API (conservatively) restricts the kinds of
messages that can be exchanged.
%
More concretely, and as mentioned in Section~\ref{sec:concrete}, we
restrict |send| (and |sandbox|) to sending string values.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
However, our implementation is accompanied by a library that provides
a more flexible standard library, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.

>>>>

JavaScript as specified by
ECMAScript~\cite{ecma}, does not have any built-in
functionality for I/O
(we denote this language as |targetLangJS|).
%
When JavaScript is embedded in web browser engines such as
Gecko or Blink, or in server-side platforms such as Node.js, additional
APIs such as the Document Object Model (DOM) or the file system
get exposed as part of the runtime system.
%
In a similar manner, we can directly implement the embedded language
|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
of the runtime and running multiple instances of the JavaScript VM in
separate OS-level threads.\footnote{
  We, indeed, do this for the Gecko implementation when considering
  Web Workers that run operate OS threads.
}
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
(Consider, for instance, a server-side web application that wishes to
create a new task for each HTTP request.)

@@

\begin{figure}
\centerline{\includegraphics[width=\columnwidth]{figs/node}}
\caption{\label{fig:node} Retrofitting Node.js JavaScript with IFC.
This example shows how our trusted monitor (left) is used to mediate
communication between two tasks for which IFC is enforced(left).}
\end{figure}
As shown in Figure~\ref{fig:node}, each IFC API call from a task is mediated
by the trusted library code (the main Node.js context), that tracks
the current label, messages, etc. of each task.
%
While V8 provides a means for sharing objects between contexts that
share a security token (in the case of Blink this is used by pages of
the same origin), our API (conservatively) restricts the kinds of
messages that can be exchanged.
%
More concretely, and as mentioned in Section~\ref{sec:concrete}, we
restrict |send| (and |sandbox|) to sending string values.
%
In our formalization, this amounts to restricting the IFC language rule
for |send| such that only strings can be shared:
%{
\newcommand{\str}{"string"}
%format tOf (e) = "\texttt{typeOf}("e")\texttt{ === \str}"
%format ttrue = "\texttt{true}"
\begin{mathpar}
\inferrule[JS-send]
{
|il canFlowTo il'|\\
|iS(id') = Q|\\
|iS' = iS [ mapsto id' (il', id,  iv) , Q ]|\\
|ie = IT te|\\
|conf tS (tOf te) -> conf tS ttrue|
}
{|
iconf iS (fullconf id il tS (iniEi (send id' il' iv)), ldots)
.->
iS'; sched step (fullconf id il tS (iniEi unit), ldots)
|}
\end{mathpar}
%}
%
However, our implementation is accompanied by a library that provides
a more flexible standard library, which, among other things,
automatically marshalls JSON objects to/from strings on each
|send|/|recv|.
